Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. A final open-database is available in the repository mentioned in the abstract. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. These are discussed at more in the following sections but differ in that they are constructed following two logics. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.

\begin{figure*}
\centering
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-1.05cm}\includegraphics[scale=1.0]{figures/budget_macc.eps}
    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
    \label{fig:MACC_budget}
\end{minipage}\qquad
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-.4cm}\includegraphics[scale=1.0]{figures/threshold_macc.eps}
    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
    \label{fig:MACC_threshold}
\end{minipage}
\end{figure*}

\subsection*{General Performance}
Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two. This is a result of those scenarios still relying on the natural-gas based heating system. This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of more severe climate are not disrupting mitigation efforts in the model. It appears to enable it to an extent. Comparing the highlighted groups of similar strategy-sets between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent. We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year.

% Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.

\begin{figure}[hbt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

>>>>

%---------------------------------------------------------------------------------------
\section*{Results}
\begin{figure}[hbpt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

\begin{figure*}[hbpt]
\centering
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-1.05cm}\includegraphics[scale=1.0]{figures/budget_macc.eps}
    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
    \label{fig:MACC_budget}
\end{minipage}\qquad
\begin{minipage}[b]{.45\textwidth}
    \hspace*{-.4cm}\includegraphics[scale=1.0]{figures/threshold_macc.eps}
    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
    \label{fig:MACC_threshold}
\end{minipage}
\end{figure*}

The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. A final open-database is available in the repository mentioned in the abstract. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. These are discussed at more in the following sections but differ in that they are constructed following two logics. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.

\subsection*{General Performance}
Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two. This is a result of those scenarios still relying on the natural-gas based heating system. This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of more severe climate are not disrupting mitigation efforts in the model. It appears to enable it to an extent. Comparing the highlighted groups of similar strategy-sets between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent. We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year. Figure \ref{fig:compare_district} shows this in the operation of the district in the baseline cases from each climate scenario
